Sequential rank agreement methods for comparison of ranked lists

### 2015-06-01 latex/paper.Rnw
Important implementation items. NOVEL

res <- sqrt(sra(inputmatrix, B=20))
inputmatrix2 <- inputmatrix
inputmatrix2[51:nrow(inputmatrix),] <- 0
res2 <- sqrt(sra(inputmatrix2, B=20))

@@

<<fig2a, fig=TRUE,echo=FALSE,include=FALSE>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
##
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

<<fig2b, fig=TRUE,echo=FALSE,include=FALSE >>=
ysize <- 80
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
##
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

<<echo=FALSE, results=hide>>=
xxx <- as.data.frame(inputmatrix[1:10,])
xxx

<<label=tab1,echo=FALSE,results=tex>>=
library(xtable)
print(xtable(xxx))
#print(xtable(xxx, caption = "Top 10 list of results", label = "tab:one",
#digits = c(0, 0, 2, 0, 2, 3, 3)), table.placement = "tbp",
#caption.placement = "top")

@@

>>>>

res <- sqrt(sra(inputmatrix, B=20))
inputmatrix2 <- inputmatrix
inputmatrix2[51:nrow(inputmatrix),] <- NA
res2 <- sqrt(sra(inputmatrix2, B=20))

@@

<<fig2a, fig=TRUE,echo=FALSE,include=FALSE,cache=TRUE>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
##
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

<<fig2b, fig=TRUE,echo=FALSE,include=FALSE,cache=TRUE >>=
ysize <- 80
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
##
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

<<label=tab1,echo=FALSE,results=tex>>=
library(xtable)
xxx <- as.data.frame(inputmatrix[1:10,])
xxx2 <- xtable(xxx)
digits(xxx2) <- 0
print(xxx2)
#print(xtable(xxx, caption = "Top 10 list of results", label = "tab:one",
#digits = c(0, 0, 2, 0, 2, 3, 3)), table.placement = "tbp",
#caption.placement = "top")

@@

In this section we apply the method to the ColonData data from the R
package MAMA (Ihnatova, 2013), which consists of gene expression
measurements from a subset of 500 genes from 77 individuals from
Denmark, 36 from Australia and 41 from Japan as well as information on
microsattelite stability (stable MSS/unstable MSI) which is often used
as an indicator for colorectal cancer. The genes were tested for
difference in expression in the MSI/MSS groups using the limma package
(Smyth, 2005). The genes were then ranked according to p–values giving
three lists that we wish to compare, the top of these can be seen in
Table 4.

<<fig=TRUE>>=
myres <- average_overlap(inputmatrix[,1:2])
myres2 <- average_overlap(inputmatrix[-1,1:2])
xvals <- 1:500
plot(myres, xlim=c(1, 500), type="l")
lines(xvals[-1], myres2, col="red")
@
